The Castro AMR Simulation Code: Current and Future Developments

### 2019-09-29 astronum_2019_Castro/astronum-castro-2019.tex
more work on the paper

\author{M. Zingale$^1$,
        J.~B. Bell$^4$,
        K.~Eiden$^1$,
        A.~Harpole$^1$,
        M.~P. Katz$^5$,
        A.~J. Nonaka$^4$,
        D.~E. Willcox$^4$, and
        W. Zhang$^4$}

@@

\address{$^2$Department of Astrophysical Sciences, Princeton University,
  Peyton Hall, Princeton, NJ 08544, USA}

\address{$^3$Mathematical Sciences and STAG Research Centre,
  University of Southampton, SO17 1BJ, UK}

\address{$^4$Center for Computational Sciences and Engineering,
  Lawrence Berkeley National Lab, Berkeley, CA 94720 USA}

\address{$^5$NVIDIA Corporation, 2788 San Tomas Expressway,
  Santa Clara, CA, 95050 USA}

@@

Castro~\cite{castro}

\section{Summary}

We did stuff

>>>>

\author{M. Zingale$^1$,
        A.~S.~Almgren$^2$,
        M.~Barrios Sazo$^1$,
        J.~B. Bell$^4$,
        K.~Eiden$^1$,
        A.~Harpole$^1$,
        M.~P. Katz$^3$,
        A.~J. Nonaka$^2$,
        D.~E. Willcox$^2$, and
        W. Zhang$^2$}

@@

\address{$^2$Center for Computational Sciences and Engineering,
  Lawrence Berkeley National Lab, Berkeley, CA 94720 USA}

\address{$^3$NVIDIA Corporation, 2788 San Tomas Expressway,
  Santa Clara, CA, 95050 USA}

@@

The \castro\ astrophysical simulation code~\cite{castro} is designed
for modeling problems in nuclear astrophysics, with the ability to
accurately capture the interplay between hydrodynamics, reactions,
gravity, and radiation in stars with complex equations of state.
Since \castro\ was first development, there have been a number of
enhancements to the code base, expanding its applicability to a new
range of scientific problems.

\castro\ has been applied to models of Type Ia supernovae,
core-collapse supernovae, pair-instability supernova, and most
recently X-ray bursts.  A common challenge in modeling these events is
the range of length and timescales involved.

To capture length scales, \castro\ uses adaptive mesh refinement,
through the \amrex\ library~\cite{amrex_joss}.

Approximations are usually made for multi-dimensional simulations.

\section{Modeling Reactive Flow}

The recent focus in \castro\ has been on high-fidelity simulations of
reactive flow.  In \cite{castro:sdc} we introduced a new time
integration strategy, spectral deferred corrections (SDC), that
eliminates the coupling error introduced by commonly used operator
splitting techniques (see the discussion in \cite{astronum:2018} for a
graphical illustration of splitting error).  The SDC algorithm used in
\castro\ follows the ideas of \cite{dutt:2000,minion:2003}, and uses
low order explicit advection and implicit reaction updates in a
correction equation that when applied iteratively achieves high-order
time-accuracy.  \castro\ implements both a second-order and
fourth-order method (in space and time) coupling reactions and
hydrodynamics.  At the moment, the method is limited to single levels.

\section{Performance Portability}

The original approach to parallelism in \castro\ was MPI + OpenMP,
with scaling on manycore architectures achieve using a tiling approach
to OpenMP~\cite{tiling}.

\section{Example Application}

The SDC approach was demonstrated in \cite{castro:sdc} through a large
suite of convergence tests and a thermonuclear flame problem.

\section{Future Developments}

MHD

Other SDC quadrature schemes / detonations

SDC multilevel + XRBs
